Reproducible Research in R: A tutorial on how to do the same thing more than once

### 2021-08-06 manuscript.Rmd
restructure discussion (headings made no sense) closes #190 closes #191

We implemented a mechanism that only uses simulated data when the actual data is not yet available  (in this example if the file `data/data.csv` does not exist)for the results section.
This mechanism also warns readers if these results are based on simulated data.
The warning is colored red to avoid any confusion between mock and actual results.
As soon as the actual data are available, the simulated data is no longer used, and the results represent the actual empirical results of the study.

@@

@@

## Limitations of repro

@@

# Limitations

Increased automation is more and more recognized as a means to improve the research process [@rouderMinimizingMistakesPsychological2019], and therefore this workflow fits well together with other innovations that employ automation, like machine-readable hypothesis tests [@lakensImprovingTransparencyFalsifiability2021] or automated data documentation [@arslanHowAutomaticallyDocument2019].
Automated and reusable research projects promise a wide range of applications, among them PAC [possibly submitted as a registered report @nosekRegisteredReports2014; @chambersWhatNextRegistered2019], Direct Replication[@simonsValueDirectReplication2014], fully automated living metanalysis [@elliottLivingSystematicReviews2014], Executable Research Articles [@elifesciencespublicationsELifeLaunchesExecutable2020], and other innovations like the live analysis of born open data [@rouderWhatWhyHow2016; @kekecsRaisingValueResearch2019].

Therefore reproducibility facilitates traditional good scientific practices and provides the foundation for promising innovations.

Please note that the statistical procedure in the PAC example of running different test procedures based on a fixed skewness threshold was created for didactic purposes and is not necessarily optimal for addressing your research question.

# Outlook

>>>>

We implemented a mechanism that only uses simulated data when the actual data is not yet available (in this example if the file `data/data.csv` does not exist) for the results section.
This mechanism also warns readers if these results are based on simulated data.
The warning is colored red to avoid any confusion between mock and actual results.
As soon as the actual data are available, the simulated data is no longer used, and the results represent the actual empirical results of the study.

@@

Increased automation is more and more recognized as a means to improve the research process [@rouderMinimizingMistakesPsychological2019], and therefore this workflow fits well together with other innovations that employ automation, like machine-readable hypothesis tests [@lakensImprovingTransparencyFalsifiability2021] or automated data documentation [@arslanHowAutomaticallyDocument2019].
Automated research projects promise a wide range of applications, among them PAC [possibly submitted as a registered report @nosekRegisteredReports2014; @chambersWhatNextRegistered2019], Direct Replication[@simonsValueDirectReplication2014], fully automated living metanalysis [@elliottLivingSystematicReviews2014], Executable Research Articles [@elifesciencespublicationsELifeLaunchesExecutable2020], and other innovations like the live analysis of born open data [@rouderWhatWhyHow2016; @kekecsRaisingValueResearch2019].

Central to these innovations is a property we call "reusability" which we hope this workflow promotes.
Reusable code can run on different inputs from a similar context and produce valid outputs.
This property is based on reproducibility but requires the researcher to more carefully write the software [@lanerganSoftwareEngineeringReusable1989] such that it is _build-for-reuse_ [@al-badareenReusableSoftwareComponents2010].
The reproducible workflow we present here is heavily automated and hence promotes reusability.
Furthermore, adhering to principles of reusability typically removes errors in the code and thus increases the likelihood that the statistical analysis is correct.
Therefore reproducibility facilitates traditional good scientific practices and provides the foundation for promising innovations.

@@

## Limitations

@@

## Outlook
